Ecological network control

### 2018-06-18 paper/supp-info.Rmd
Variable importance table for species level model

```
```

>>>>

```{r tab-var-importance}
cc_imp <- get_var_importance(species_model_cc$fixed) 
su_imp <- get_var_importance(species_model_superior$fixed)

dplyr::bind_rows(cc_imp, su_imp) %>%
  dplyr::mutate(term = pretty_term_names(term)) %>%
  knitr::kable("latex", 
               booktabs = T, 
               row.names = F, 
               digits = 2, 
               escape = F, 
               caption = "Variable importance for each set of models. The importance is the sum of the weights of all models in which the variable was included.",
               linesep = '') %>%
  kableExtra::kable_styling(font_size = 8)%>%
  kableExtra::group_rows("control capacity models", 1, nrow(cc_imp)) %>%
  kableExtra::group_rows("superior probability models", nrow(cc_imp) + 1, nrow(cc_imp) + nrow(su_imp))
```
